Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-01-22 joss/paper.Rmd
Debugs JOSS code snippets and renders paper.md
edits to JOSS intro and discussion

The growth of programming in the sciences has been explosive in the
last decade. In particular, the statistical programming language ``R``
has grown exponentially to become one of the top ten programming
languages in use today. Recently, concerns have arisen over the
reproducibility of scientific research [@Peng2011 @Baker2016
@Stodden2018] and the potential issues stemming from the complexity
and fragility of analytical software [@Pasquier2017 @Chen2018]. There
is now a recognition that simply making the code open is not enough,
and that there is a need for improvements to documentation and
transparency [@Chen2018].

@@

@@

clean(script.long, "fit.sqrt.A")

>>>>

The growth of programming in the sciences has been explosive in the
last decade. In particular, the statistical programming language ``R``
has grown exponentially to become one of the top ten programming
languages in use today. Increasingly, concerns have arisen over the
reproducibility of scientific research [@Peng2011 @Baker2016
@Stodden2018] and the potential issues stemming from the complexity
and fragility of analytical software [@Pasquier2017]. There is now a
recognition that simply making the code open is not enough, and that
there is a need for improvements to documentation and transparency
[@Pasquier2018].

@@

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")
script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")

@@

clean(script.long, "fit_sqrt_A")
